% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
%
% (c) 2012 Scott Clark <sc932@cornell.edu> cam.cornell.edu/~sc932
%
%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,10pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage{hyperref}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
%\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubheadinged}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4}\\
\end{tabular*}\vspace{-6pt}}

%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Tanvi Surana}\\
\href{http://tanvi-surana.github.io/}{tanvi-surana.github.io}\\
tanvisurana20@gmail.com
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Education}
\begin{itemize}
\item
\ressubheadinged{Indira Gandhi Delhi Technical University}{Delhi}{B.Tech Computer Science and Engineering}{August 2013 - Present}
    
    \begin{itemize}
	\resitem{Performance: 82\%, 6 Semesters}
    \end{itemize}
\end{itemize}

\begin{itemize}
\item
\ressubheadinged{Delhi Public School Rohini}{Delhi}{C.B.S.E, AISSCE}{}
    \begin{itemize}
	\resitem{Performance: 91.6\%}
    \end{itemize}
\end{itemize}


\resheading{Projects}
\begin{itemize}

\item
	\ressubheading{Lifetime Of Wireless Sensor Networks}{Self}{Self}{Ongoing}
	\begin{itemize}
		\resitem{Increasing Lifetime of Wireless Sensor Networks}
	\end{itemize}
	
\item
	\ressubheading{Jewellery Website}{Self}{Self}{2016}
	\begin{itemize}
		\resitem{A Jewellery website that displays various products with customized user authorization system.  (Django,LESS)}
	\end{itemize}

\item
	\ressubheading{Smart Secure}{Self}{Self}{2016}
	\begin{itemize}
		\resitem{A Raspberry Pi2 based home automation product that uses a GUI for user interaction. The device is a smart
locker that alerts the owner in case of misuse of the locker. In case of an invalid login, the owner is alerted with
mail containing the photograph of the user. Immediately a call is placed and message is also sent. (Raspberry Pi2,Python)}
	\end{itemize}

\item
	\ressubheading{Smart Bin}{Self}{Self}{2015}
	\begin{itemize}
		\resitem{Web app that had been designed to aid the volunteers of the NGO Reap Benefit based in Bengaluru to
automate the tracking of dustbins fitted with sensors and educates the public for waste segregation activities.
The application collected the data from sensors thus, helping volunteers analyze data using graphs. The app
also displayed the shortest path between various bins at different localities.
(Python, Django, Bootstrap, Google Maps API, D3.js, PostgreSQL)}
	\end{itemize}
	
\item
	\ressubheading{2048 Game}{Self}{Self}{2014}
	\begin{itemize}
		\resitem{Interactive version of the 2048 game made using web technologies. It works on the keyboard click events with
changing colors and displaying the highest score.
(HTML, CSS, JavaScript)}
	\end{itemize}	

\end{itemize}

\resheading{Skills}
\begin{itemize}
\item \textbf{Languages:} C, C++, Git, Python, HTML, CSS, LESS, Javascript.

\item \textbf{Framework:} Django

\item \textbf{Basic Knowledge:} Cloudsim (Cloud Computing) and Network Programming.

\end{itemize}

\resheading{Volunteer}
\begin{itemize}

\item
	\ressubheading{Learn IT Girl!}{Remote}{Mentor}{Mentor, Feb 2016 to April 2016}
	\begin{itemize}
		\resitem{Mentoring a student learn C++.}
	\end{itemize}
\end{itemize}



\resheading{Achievements \& Awards}
\begin{itemize}
	\item Second Prize, Developers at Work, Technical Fest (CSI-IGDTUW).
    
	\item Scholar, Gold-Medalist, Silver-Medalist for excellent academic performance in school 
University, 2010.
\end{itemize}


\end{document}
